Multilevel generalizations of collective spin dynamics and squeezing

### 2019-10-17 collective_sun/multilevel_spin_notes.tex
moved the discussion of collective states to a subsection on the interaction Hamiltonian

\newcommand{\MSC}{\text{MSC}}

@@

\title{Multi-level generalizations of collective spin dynamics and
  squeezing}%
\author{Michael A. Perlin}%
\date{\today}

@@

We consider a collection of $n$-level fermions on a 1-D lattice, with
a single-particle Hamiltonian
\begin{align}
  H_{\t{lat}} = -J \sum_{q,\mu} \cos\p{qa} c_{q\mu}^\dag c_{q\mu},
  \label{eq:H_lat}
\end{align}
where $J$ is the nearest-neighbor tunneling rate, $a$ is the spacing
between neighboring lattice sites, and $c_{q\mu}$ is the fermionic
annihilation operator for a particle in quasi-momentum mode $q$ with
internal state (e.g.~nuclear spin) $\mu$.  Under the frozen-mode
approximation, collective two-body SU($n$)-symmetric interactions
between these fermions take form\cite{perlin2019effective}
\begin{align}
  H_{\t{int}} = \f{u}{2} \sum_{p,q,\mu,\nu}
  \p{c_{p\mu}^\dag c_{q\nu}^\dag c_{q\nu} c_{p\mu}
    + c_{q\mu}^\dag c_{p\nu}^\dag c_{q\nu} c_{p\mu}},
\end{align}
where $u\equiv U/L$ is the two-body on-site interaction energy $U$
divided by the number of lattice sites $L$.  Defining the spin
operators $S_{\mu\nu}^{(p)}\equiv c_{p\mu}^\dag c_{p\nu}$ for each
quasi-momentum $p$, we can alternately write
\begin{align}
  H_{\t{int}} = \f{u}{2} \sum_{p,q,\mu,\nu}
  \p{S_{\mu\mu}^{(p)} S_{\nu\nu}^{(q)} - S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}}
  = \f{u}{2}\p{N^2 - \sum_{p,q,\mu,\nu}
    S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}},
\end{align}
where $N$ is the total number of particles.  In the absence of
coherence between sectors of different particle number, we can neglect
the $\sim N^2$ term and simply write
\begin{align}
  H_{\t{int}}
  = - \f{u}{2} \sum_{p,q,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}.
\end{align}
In the case of SU(2), at this point we would expand the spin operators
$S_{\mu\nu}^{(p)}$ in terms of Pauli operators in order to convert
$H_{\t{int}}$ into an SU(2) spin Hamiltonian\cite{he2019engineering}.
To generalize this procedure to the case of SU($n$), we first define a
vector $\v S^{(p)}$ of all spin operators $S_{\mu\nu}^{(p)}$, and
write
\begin{align}
  H_{\t{int}}
  = - \f{u}{2} \sum_{p,q} {\v S^{(p)}}^\dag \c \v S^{(q)}
  = - \f{u}{2} \v\S^\dag \c \v\S,
  &&
  \v\S\equiv \sum_p \v S^{(p)}.
  \label{eq:H_int_spin}
\end{align}
In the remainder of this section, we identify various bases for the
space of linear operators on the Hilbert space $\H_n$ of an $n$-level
system.  For brevity, we denote this space of operators by
$\B\p{\H_n}$, and note that $\B\p{\H_n}$ is itself an
$n^2$-dimensional Hilbert space equipped with a trace
(Hilbert-Schmidt) inner product
\begin{align}
  \obk{\O|\Q} \equiv \tr\p{\O^\dag Q},
\end{align}
where $\oket{\Q}$ and $\obra{\O}$ respectively denote vectors in
$\B\p{\H_n}$ and its dual space $\B\p{\H_n}^*$.  Similarly to the set
of all spin operators $S_{\mu\nu}\equiv\op{\mu}{\nu}$ on the
single-particle Hilbert space at each quasi-momentum, all of the bases
we consider will be orthonormal with respect to the trace inner
product.  As we show in Appendix \ref{sec:changing_bases}, the
collective SU($n$)-symmetric interaction Hamiltonian in
\eqref{eq:H_int_spin} takes an identical form in any orthonormal basis
for $\B\p{\H_n}$.

@@

Weyl operators\cite{bertlmann2008bloch} and self-adjoint linear
combinations thereof\cite{asadian2016heisenbergweyl} also provide an
interesting basis of operators for finite-dimensional Hilbert spaces.
These operators are related to the notions of position, momentum, and
phase-space displacement in a discrete space.  As our present work is
motivated by multi-level systems that are realized with nuclear spin
(angular momentum) degrees of freedom, however, the transition and
drive operators are more natural to use than the Weyl operators, so we
will not discuss Weyl operators any further.

@@

A driving laser addressing spin-$1/2$ fermions on a 1-D lattice will
induce the Hamiltonian
\begin{align}
  \left. H_{\t{drive}}^{(\phi)} \right|_{n=2}
  = \Omega \sum_j
  \p{e^{i\phi j} c_{j,\up}^\dag c_{j,\dn}
    + e^{-i\phi j} c_{j,\dn}^\dag c_{j,\up}},
  \label{eq:H_drive_2}
\end{align}
where $\Omega$ is a (real) driving amplitude, $j\in\mathbb{Z}$ indexes
a lattice site, and $\phi$ is the relative phase of the drive between
adjacent lattice sites.  The multi-level analogue of
\eqref{eq:H_drive_2} is
\begin{align}
  H_{\t{drive}}^{(\phi)}
  = -\Omega \sum_j \p{e^{i\phi j} T_{1,1}^{(j)}
    + e^{-i\phi j} {T_{1,1}^{(j)}}^\dag}
  = \Omega \D_{1,1}^{(\phi)},
  \label{eq:H_drive}
\end{align}
where
\begin{align}
  \D_{LM}^{(\phi)}
  \equiv \sum_j \sp{\cos\p{M\phi j} D_{LM}^{(j)}
    - \sin\p{M\phi j} D_{L,-M}^{(j)}},
  \label{eq:drive_rot}
\end{align}
is an inhomogeneously rotated collective drive operator.  We can make
this drive spatially homogenous via the gauge transformation
$c_{j\mu}^\dag \to e^{-i\mu\phi j} c_{j\mu}^\dag$, which takes
 \begin{align}
  H_{\t{drive}}^{(\phi)} \to H_{\t{drive}} = \Omega \D_{1,1},
  &&
  \D_{LM} \equiv \D_{LM}^{(0)} = \sum_j D_{LM}^{(j)}.
\end{align}
The SU($n$) symmetry of collective interactions implies that the
interaction Hamiltonian $H_{\t{int}}$ in \eqref{eq:H_int_drive} is
invariant under this gauge transformation, but the single-particle
Hamiltonian in \eqref{eq:H_lat} transforms as (see Appendix
\ref{sec:lat_drive})
\begin{align}
  H_{\t{lat}}
  \to H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa+\mu\phi} c_{q\mu}^\dag c_{q\mu}
  = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  \label{eq:H_lat_SOC}
\end{align}
with effective inhomogeneous driving field amplitudes
\begin{align}
  B_L^{(\phi,q)} = -J w_L\p{qa} A_L^{(\phi)},
\end{align}
where
\begin{align}
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  &&
  A_L^{(\phi)} \equiv \p{-1}^L \sqrt{\f{2L+1}{2I+1}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Spin-orbit coupling with multi-level systems thus allows for the
simulation of synthetic gauge fields with large spin ($L>1$).  As we
will see in the following section, multi-laser drives can also
simulate synthetic large-spin fields with non-zero spin projection
($M\ne0$) onto a quantization axis.

@@

Rather than coupling the states of a multi-level system directly with
a single driving laser, as in Section \ref{sec:drive_SOC}, we now

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Collective states}
\label{sec:collective}

Given a quantum system composed of $N$ identical (but distinguishable)
$n$-level subsystems, e.g.~an array of $n$-level nuclear spins, we
identify the set $\Pi\equiv\set{\Pi_\sigma}$ of operators that permute
subsystems, labeled by corresponding elements $\sigma\in\SS_N$ of the
symmetric group $\SS_N$ of order $N$.  We refer to simultaneous
eigenstates of all $\Pi_\sigma\in\Pi$ as {\it collective states}.  The
subset of collective states that have eigenvalue $1$ with respect to
all permutation operators $\Pi_\sigma\in\Pi$ is the {\it maximally
  symmetric collective (MSC)} manifold $\M_\MSC$, which is precisely
the Dicke manifold in the case of two-level subsystems ($n=2$).  The
MSC manifold is spanned by a basis $\set{\ket{\v m}}$ of MSC states
that can be uniquely identified by a list of integers
$\v m=\p{m_0,m_1,\cdots,m_{n-1}}\in\ZZ_{N+1}^n$, where $m_k$ indicates
the total occupation number of subsystem state $k$, and
$\sum_k m_k=N$.  The Dicke manifold of $N$ qubits, for example, is
spanned by the Dicke states $\set{\ket{m_0,m_1}}$, where $m_0+m_1=N$
and the integer $m_0$ ($m_1$) indicates the occupation number of the
qubit state $\ket{0}$ ($\ket{1}$).  The dimension of the MSC manifold
is determined by the number of ways to assign $N$ sub-systems to $n$
states, which is ${N+n-1 \choose n-1}$.

The MSC manifold has two key properties.  First, the MSC manifold is
closed under the action of unitaries generated by collective drive
operators $\D_{LM}$, as well as linear combinations and products
thereof.  Closure of the MSC manifold under collective dynamics is a
straightforward consequence of the permutational symmetry obeyed by
collective operators.  Second, the MSC manifold is the ground-state
manifold of the collective SU($n$)-symmetric interaction Hamiltonian
$H_{\t{int}}$ in \eqref{eq:H_int_spin}.  To illuminate the spectral
properties of $H_{\t{int}}$, we can expand
\begin{align}
  H_{\t{int}}
  = -\f{u}{2} \sum_{p,q,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}
  = -u\sum_{\substack{p<q\\\mu,\nu}} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}
  - \f{u}{2} \sum_{p,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(p)}
  = -u\sum_{p<q} \Pi_{pq} - \f12 N n u
  \simeq -u\sum_{p<q} \Pi_{pq},
  \label{eq:H_int_perm}
\end{align}
where $\Pi_{pq}\in\Pi$ permutes subsystems $p$ and $q$, and $\simeq$
denotes equality up to an overall constant with no physical
consequence.  The form of $H_{\t{int}}$ in \eqref{eq:H_int_perm}
reveals that its eigenstates can be classified by their symmetries
under the permutation of subsystems.  In particular, the ground-state
manifold of $H_{\t{int}}$ consists of states that have eigenvalue 1
with respect to all pair-wise permutation operators $\Pi_{pq}$, which
is precisely the MSC manifold $\M_\MSC$.  The interaction energy of
states $\ket{\psi_\MSC}\in\M_\MSC$ is (up to an overall constant)
simply $-{ N\choose 2 } u = -\p{1/4}N\p{N-1} u$.

>>>>

\newcommand{\FS}{\text{FS}}

@@

\title{Multilevel generalizations of collective spin dynamics and
  squeezing}%
\author{Michael A. Perlin}%
\date{\today}

@@

We consider a collection of $n$-level fermions on a 1-D lattice, with
a single-particle Hamiltonian
\begin{align}
  H_{\t{lat}} = -J \sum_{q,\mu} \cos\p{qa} c_{q\mu}^\dag c_{q\mu},
  \label{eq:H_lat}
\end{align}
where $J$ is the nearest-neighbor tunneling rate, $a$ is the spacing
between neighboring lattice sites, and $c_{q\mu}$ is the fermionic
annihilation operator for a particle in quasi-momentum mode $q$ with
internal state (e.g.~nuclear spin) $\mu$.  Under the frozen-mode
approximation, collective two-body SU($n$)-symmetric interactions
between these fermions take form\cite{perlin2019effective}
\begin{align}
  H_{\t{int}} = \f{u}{2} \sum_{p,q,\mu,\nu}
  \p{c_{p\mu}^\dag c_{q\nu}^\dag c_{q\nu} c_{p\mu}
    + c_{q\mu}^\dag c_{p\nu}^\dag c_{q\nu} c_{p\mu}},
\end{align}
where $u\equiv U/L$ is the two-body on-site interaction energy $U$
divided by the number of lattice sites $L$.  Defining the spin
operators $S_{\mu\nu}^{(p)}\equiv c_{p\mu}^\dag c_{p\nu}$ for each
quasi-momentum $p$, we can alternately write
\begin{align}
  H_{\t{int}} = \f{u}{2} \sum_{p,q,\mu,\nu}
  \p{S_{\mu\mu}^{(p)} S_{\nu\nu}^{(q)} - S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}}
  = \f{u}{2}\p{N^2 - \sum_{p,q,\mu,\nu}
    S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}},
\end{align}
where $N$ is the total number of particles.  In the absence of
coherence between sectors of different particle number, we can neglect
the $\sim N^2$ term and simply write
\begin{align}
  H_{\t{int}}
  = - \f{u}{2} \sum_{p,q,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}.
\end{align}
In the case of SU(2), at this point we would expand the spin operators
$S_{\mu\nu}^{(p)}$ in terms of Pauli operators in order to convert
$H_{\t{int}}$ into an SU(2) spin Hamiltonian\cite{he2019engineering}.
To generalize this procedure to the case of SU($n$), we first define a
vector $\v S^{(p)}$ of all spin operators $S_{\mu\nu}^{(p)}$, and
write
\begin{align}
  H_{\t{int}}
  = - \f{u}{2} \sum_{p,q} {\v S^{(p)}}^\dag \c \v S^{(q)}
  = - \f{u}{2} \v\S^\dag \c \v\S,
  &&
  \v\S\equiv \sum_p \v S^{(p)}.
  \label{eq:H_int_spin}
\end{align}
In the bulk of this section, we identify various bases for the space
of linear operators on the Hilbert space $\H_n$ of an $n$-level
system.  For brevity, we denote this space of operators by
$\B\p{\H_n}$, and note that $\B\p{\H_n}$ is itself an
$n^2$-dimensional Hilbert space equipped with a trace
(Hilbert-Schmidt) inner product
\begin{align}
  \obk{\O|\Q} \equiv \tr\p{\O^\dag Q},
\end{align}
where $\oket{\Q}$ and $\obra{\O}$ respectively denote vectors in
$\B\p{\H_n}$ and its dual space $\B\p{\H_n}^*$.  Similarly to the set
of all spin operators $S_{\mu\nu}\equiv\op{\mu}{\nu}$ on the
single-particle Hilbert space at each quasi-momentum, all of the bases
we consider will be orthonormal with respect to the trace inner
product.  As we show in Appendix \ref{sec:changing_bases}, the
collective SU($n$)-symmetric interaction Hamiltonian in
\eqref{eq:H_int_spin} takes an identical form in any orthonormal basis
for $\B\p{\H_n}$.

@@

Weyl operators\cite{bertlmann2008bloch} and self-adjoint linear
combinations thereof\cite{asadian2016heisenbergweyl} also provide an
interesting basis of operators for finite-dimensional Hilbert spaces.
These operators are related to the notions of position, momentum, and
phase-space displacement in a discrete space.  As our present work is
motivated by multilevel systems that are realized with nuclear spin
(angular momentum) degrees of freedom, however, the transition and
drive operators are more natural to use than the Weyl operators, so we
will not discuss Weyl operators any further.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsystem permutations and the fully symmetric manifold}
\label{sec:perm_ops}

For our final re-expression of collective SU($n$)-symmetric
interactions, we abandon the use of single-spin operators entirely to
express the interaction Hamiltonian $H_{\t{int}}$ in terms of
operators that permute tensor factors (subsystems) of a Hilbert space
with an $N$-fold tensor product structure (e.g.~an array of nuclear
spins).  Specifically, we denote the Hilbert space of an $n$-level
system by $\H_n$, denote its $N$-fold tensor product by
$\H_n^{\otimes N}$, and identify the set $\Pi\equiv\set{\Pi_\sigma}$
of operators that permute tensor factors of $\H_n^{\otimes N}$
according to elements $\sigma\in\SS_N$ of the symmetric group of order
$N$.  We then expand
\begin{align}
  H_{\t{int}}
  = -\f{u}{2} \sum_{p,q,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}
  = -u\sum_{\substack{p<q\\\mu,\nu}} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}
  - \f{u}{2} \sum_{p,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(p)},
  \label{eq:H_int_perm_start}
\end{align}
where the first sum,
\begin{align}
  \sum_{\substack{p<q\\\mu,\nu}} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(q)}
  = \sum_{\substack{p<q\\\mu,\nu}} \op{\mu}{\nu}^{(p)} \op{\nu}{\mu}^{(q)}
  = \sum_{\substack{p<q\\\mu,\nu}} \op{\mu\nu}{\nu\mu}^{(p,q)}
  = \sum_{p<q} \Pi_{pq}
  \label{eq:spin_perm}
\end{align}
is simply a sum over all permutations $\Pi_{pq}$ of subsystems $p$ and
$q$; and
\begin{align}
  \sum_{p,\mu,\nu} S_{\mu\nu}^{(p)} S_{\nu\mu}^{(p)}
  = \sum_{p,\mu,\nu} \op{\mu}{\nu}^{(p)} \op{\nu}{\mu}^{(p)}
  = n \sum_{p,\mu} \op{\mu}{\mu}^{(p)}
  = n \sum_p \1^{(p)}
  = n N
  \label{eq:spin_const}
\end{align}
is merely a constant.  Substituting \eqref{eq:spin_perm} and
\eqref{eq:spin_const} into \eqref{eq:H_int_perm_start} yields
\begin{align}
  H_{\t{int}} = -u \sum_{p<q} \Pi_{pq} - \f12 N n u
  \simeq -u\sum_{p<q} \Pi_{pq},
  \label{eq:H_int_perm}
\end{align}
where $\simeq$ denotes equality up to an overall constant with no
physical consequence.  The form of the interaction Hamiltonian
$H_{\t{int}}$ makes it evident that its ground-state manifold
$\M_{\FS}$ is the set of {\it fully symmetric} (FS) states that have
eigenvalue $1$ with respect to all pairwise permutation operators
$\Pi_{pq}$, and thereby also all $\Pi_\sigma\in\Pi$.  The fully
symmetric manifold $\M_\FS\subset\H_n^{\otimes N}$ is spanned by a
basis $\set{\ket{\v m}}$ of fully symmetric states that can be
uniquely identified by a list of integers
$\v m\equiv\p{m_0,m_1,\cdots,m_{n-1}}\in\ZZ_{N+1}^n$, where $m_s$
indicates the total occupation number of subsystem state $s$, and
$\sum_sm_s=N$.  In the case of $n=2$, the fully symmetric manifold
$\M_\FS$ is precisely the Dicke manifold\cite{dicke1954coherence} of
$N$ qubits, spanned by Dicke states $\set{\ket{m_0,m_1}}$ for which
$m_0+m_1=N$ and the integer $m_0$ ($m_1$) indicates the total
occupation number of qubit state $\ket{0}$ ($\ket{1}$).  The dimension
of fully symmetric manifold $\M_\FS$ is determined by the number of
ways to assign $N$ subsystems to $n$ states, which is
${N+n-1 \choose n-1}$, and energy of $\ket{\psi_\FS}\in\M_\FS$ with
respect to the interaction Hamiltonian $H_{\t{int}}$ in
\eqref{eq:H_int_perm} is $-u{N \choose 2}=-\p{1/4}N\p{N-1}u$.

In addition to the fact that the fully symmetric manifold $\M_\FS$ is
ground-state manifold of the interaction Hamltonian $H_{\t{int}}$, an
important feature of $\M_\FS$ is that it is closed under the action of
unitaries generated by collective operators of the form
$\Q=\sum_pQ^{(p)}$, as well as linear combinations and products
thereof.  Closure of $\M_\FS$ under collective dynamics is a
straightforward consequence of the permutational symmetry obeyed by
collective operators.

@@

A driving laser addressing spin-$1/2$ fermions on a 1-D lattice will
induce the Hamiltonian
\begin{align}
  \left. H_{\t{drive}}^{(\phi)} \right|_{n=2}
  = \Omega \sum_j
  \p{e^{i\phi j} c_{j,\up}^\dag c_{j,\dn}
    + e^{-i\phi j} c_{j,\dn}^\dag c_{j,\up}},
  \label{eq:H_drive_2}
\end{align}
where $\Omega$ is a (real) driving amplitude, $j\in\mathbb{Z}$ indexes
a lattice site, and $\phi$ is the relative phase of the drive between
adjacent lattice sites.  The multilevel analogue of
\eqref{eq:H_drive_2} is
\begin{align}
  H_{\t{drive}}^{(\phi)}
  = -\Omega \sum_j \p{e^{i\phi j} T_{1,1}^{(j)}
    + e^{-i\phi j} {T_{1,1}^{(j)}}^\dag}
  = \Omega \D_{1,1}^{(\phi)},
  \label{eq:H_drive}
\end{align}
where
\begin{align}
  \D_{LM}^{(\phi)}
  \equiv \sum_j \sp{\cos\p{M\phi j} D_{LM}^{(j)}
    - \sin\p{M\phi j} D_{L,-M}^{(j)}},
  \label{eq:drive_rot}
\end{align}
is an inhomogeneously rotated collective drive operator.  We can make
this drive spatially homogenous via the gauge transformation
$c_{j\mu}^\dag \to e^{-i\mu\phi j} c_{j\mu}^\dag$, which takes
 \begin{align}
  H_{\t{drive}}^{(\phi)} \to H_{\t{drive}} = \Omega \D_{1,1},
  &&
  \D_{LM} \equiv \D_{LM}^{(0)} = \sum_j D_{LM}^{(j)}.
\end{align}
The SU($n$) symmetry of collective interactions implies that the
interaction Hamiltonian $H_{\t{int}}$ in \eqref{eq:H_int_drive} is
invariant under this gauge transformation, but the single-particle
Hamiltonian in \eqref{eq:H_lat} transforms as (see Appendix
\ref{sec:lat_drive})
\begin{align}
  H_{\t{lat}}
  \to H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa+\mu\phi} c_{q\mu}^\dag c_{q\mu}
  = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  \label{eq:H_lat_SOC}
\end{align}
with effective inhomogeneous driving field amplitudes
\begin{align}
  B_L^{(\phi,q)} = -J w_L\p{qa} A_L^{(\phi)},
\end{align}
where
\begin{align}
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  &&
  A_L^{(\phi)} \equiv \p{-1}^L \sqrt{\f{2L+1}{2I+1}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Spin-orbit coupling with multilevel systems thus allows for the
simulation of synthetic gauge fields with large spin ($L>1$).  As we
will see in the following section, multi-laser drives can also
simulate synthetic large-spin fields with non-zero spin projection
($M\ne0$) onto a quantization axis.

@@

Rather than coupling the states of a multilevel system directly with a
single driving laser, as in Section \ref{sec:drive_SOC}, we now

@@
